---
title: "Replace me"
author: "By Patrick Lorch"
code_folding: "hide"
output:
    html_document:
        toc: true
        depth: 3
---


## Rename files

Use this section if you want to rename files first, before extracting tags.

Before this step, I noticed that there were images duplicated in WC1388 10.25-11.23.19 tagged\101EK113 that were already in WC1388 10.25-11.23.19 tagged\100EK113.  They were tagged differently, so I went with copy that had NOTHING instead of blank.  I deleted copies from WC1388 10.25-11.23.19 tagged\100EK113 and left the ones in WC1388 10.25-11.23.19 tagged\101EK113 before running the renaming.

I like to rename images to have sensible names.  I probably should have renamed stations something shorter.

You can also add species classification to filename from metadata with `camtrapR::appendSpeciesNames()`

```{r rename}
require(camtrapR)

# paths must have forward slashes, no backslashes
indir="P:/WCtrailMonitoring" # These need to be renamed something to match your use case
outdir="P:/WCtrailMonitoringRenamed" # Cannot be written to same as above (or subdirectory)
projname = sapply(strsplit(indir,"/"),"[[",2)

exifTagNames(inDir = indir, returnMetadata = F)
exifTagNames(inDir = indir, returnMetadata = T)

imageRename(inDir = indir,
            outDir = outdir,
            hasCameraFolders= FALSE,
            copyImages= T, # Run first with this set to F
            writecsv = T # Run first with this set to F
)
```


## Record table extract tags

If I understand what minDeltaTime = 0 and removeDuplicateRecords =T means, 

* all records are independent,
* but any of same species with same timestamp are removed. 
* So are any that are not tagged
* We settled on using minDeltaTime = 1 to eliminate duplicates that did not have same timestamp

I am currently using indir to derive the project name.

minDeltaTime is also added to the recordtable before it is saved


```{r recordtable}
require(camtrapR)

# These need to be renamed something to match your use case
# If you do not rename files, set to indir and outdir
# Path must have forward slashes, no backslashes
indir2 = "P:/WCtrailMonitoringRenamed" 
# Cannot be written to same as above (or subdirectory)
outdir2 = "data/recordTables" 
dir.create(file.path(outdir2), showWarnings = FALSE)
# rt_out = "WCmonitoring.10to12.19.deltat10.rt.csv"

rt_gen = function(indir = indir2,
                 outdir = outdir2,
                 projname = projname,
                 mindelt = 10) {
    rt = recordTable(inDir = indir2, 
                IDfrom = "metadata",
                minDeltaTime = mindelt,
                deltaTimeComparedTo = "lastIndependentRecord",
                timeZone = "EST",
                stationCol = "Station", # leave alone
                writecsv = FALSE,
                outDir = outdir2,
                 # leave as vertical bar
                metadataHierarchyDelimitor = "|", 
                metadataSpeciesTag = "SPECIES",
                additionalMetadataTags =
                    c("GPSLatitude","GPSLongitude"),
                removeDuplicateRecords = TRUE
                )
# Add some stuff and then output
    rt$ProjectName = projname
    rt$mindeltatime = mindelt
    drange = range(rt$Date)
    daterange = paste(drange[1], drange[2], sep = " to ")
    rt_out = paste0(projname, ".",
                    daterange, ".",
                    "mindeltat", ".",
                    mindelt, ".rt.csv"
                    )
    write.csv(rt, 
          file.path(outdir2, rt_out),
          row.names = T)
    return(rt)
    }

# Trying different minDeltaTimes to see what effect it has on sample size
mindelt = 0  # minutes assumed
WCmonitoring.10to12.19.deltat0.rt =
    rt_gen(indir = indir2,
           outdir = outdir2,
           projname = projname,
           mindelt = 0)

mindelt = 1  # minutes assumed
WCmonitoring.10to12.19.deltat1.rt =
    rt_gen(indir = indir2,
           outdir = outdir2,
           projname = projname,
           mindelt = 1)

mindelt = 2  # minutes assumed
WCmonitoring.10to12.19.deltat2.rt =
    rt_gen(indir = indir2,
           outdir = outdir2,
           projname = projname,
           mindelt = 2)

mindelt = 10  # minutes assumed
WCmonitoring.10to12.19.deltat10.rt =
    rt_gen(indir = indir2,
           outdir = outdir2,
           projname = projname,
           mindelt = 10)
```


## Summarizing into tables

```{r summary}
library(dplyr)

wc_monitor.deltat1.stationbyspecies.sum = 
    WCmonitoring.10to12.19.deltat1.rt %>%
    group_by(Station,Species) %>%
    tally()
write.csv(wc_monitor.deltat1.stationbyspecies.sum, 
          file.path(outdir2,
              "wc_monitor.deltat1.stationbyspecies.sum.csv"))

```

